Dependently Typed Multi-stage Calculus

### 2019-11-26 slides/main.tex
Slides on types of LTP.

@@

\newcommand{\toc}[0]{
  \begin{frame}{Contents}
  \tableofcontents[currentsection]
  \end{frame}
}

@@

@@

@@

    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 # let vadd3 = vadd-gen 3;;
 val vadd3 : (Vec -> Vec -> Vec) code
 (* vadd3 v w =                             *)
 (*   let (v, w)=(.~v, ,~w) in              *)
 (*   .< [v[0]+w[0];v[1]+w[1];v[2]+w[2]] >. *)
    \end{verbatim}
    \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
    Enable using normal values in code values
    \begin{center}
        \( \textbf{let}\ \underbrace{\text{mul5}}_{\text{normal value}}\ x = 5 * x\ \textbf{in} \underbrace{\TB\ (\% \text{mul5}\ 4)}_{\text{code value}} \)
    \end{center}
    CSP symbol \( \% \) {\bf{lift up}} an normal value into code value.
\end{frame}

>>>>

% Settings of Table of Contents page.
% Append underline to currentsection.
% https://tex.stackexchange.com/questions/280813/beamer-change-color-underline-but-do-not-hide-shade-other-section-in-table-of-c/283585
% https://tex.stackexchange.com/questions/414250/numbers-shading-and-alert-in-beamer-table-of-contents
% Page 101 of http://tug.ctan.org/macros/latex/contrib/beamer/doc/beameruserguide.pdf
\setbeamertemplate{section in toc}{
    \inserttocsectionnumber.\ \bf{\underline{\inserttocsection}}
}
\setbeamertemplate{section in toc shaded}{
    \inserttocsectionnumber.\  \inserttocsection
}

@@

@@

% I don't use sigma in this slides.
\renewcommand{\V}{\vdash}

@@

\begin{frame}{Contents}

    \setbeamertemplate{section in toc}{
        \inserttocsectionnumber.\ \inserttocsection
    }

    \tableofcontents
    \note{
    }
\end{frame}

@@

    \begin{verbatim}
 val vadd-gen : Int -> (Vec -> Vec -> Vec) code
 # let vadd3 = vadd-gen 3;;
 val vadd3 : (Vec -> Vec -> Vec) code
 (* vadd3 v w =                            *)
 (*   < let (v, w)=(~v, ~w) in             *)
 (*      [v[0]+w[0];v[1]+w[1];v[2]+w[2]] > *)
    \end{verbatim}
    \note{
    }
\end{frame}

@@

\begin{frame}[fragile]{What is a stage?}
    Level of nested quote
    \begin{center}
        \( \underbrace{(\textbf{run}\ (\TB\ \overbrace{(2 + 3)}^{\let\scriptstyle\textstyle\substack{\text{stage }1}})) + 1}_{\let\scriptstyle\textstyle\substack{\text{stage }0}} \)
    \end{center}

    Typing judgements of \LTP include a stage.
    \begin{center}
    \( \G \vdash 2 + 3 : \I @ 1 \)
    \end{center}
    \note{
    }
\end{frame}

\begin{frame}[fragile]{Typing Rules of \LMD}
    Cannot apply a term to a function in a different stage.
    \begin{center}
        {\small \infrule[\TApp]{
            \G\V M:\sigma \to \tau @ n \andalso
            \G\V N:\sigma @ n
        }{
            \G\V M\ N : \tau @ n
        }}
    \end{center}
    Increase and decrease stage using \( \TB \) and \( \TBL \).
    \begin{center}
        {\small \infrule[{\TTB}]{
            \G\V M:\tau @ n+1
        }{
            \G\V\TB M:\TW \tau @ n
        } \hfil
        \infrule[{\TTBL}]{
            \G\V M:\TW \tau @ n
        }{
            \G\V\TBL M:\tau @ n + 1
        }}
    \end{center}
    \note{
        Let's have a look on some typing rules.
    }
\end{frame}

\begin{frame}[fragile]{Cross Stage Persistence (CSP)}
    Enable using terms at lower stages at higer stages. \\[3mm]

    Want to use \( \text{mul5} \) in a code value.
    \begin{center}
        \( \textbf{let}\ \underbrace{\text{mul5}}_{\text{stage }0}\ x = 5 * x\ \textbf{in} \TB\ \underbrace{(\% \text{mul5}\ 4)}_{\text{stage }1} \)
    \end{center}
    CSP symbol \( \% \) {\bf{lift up}} an normal value into code value.
\end{frame}
